---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
library(reconqdata)

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# Qualitative study on collaboration in Polish science 

<!-- badges: start -->
<!-- badges: end -->


This an R package

# Data

Available in CSV format:

- [Nodes and their attributes (CSV)](https://github.com/recon-icm/reconqdata/blob/master/data-raw/nodes.csv)
- [Collaboration ego-networks edgelist (CSV)](https://github.com/recon-icm/reconqdata/blob/master/data-raw/collaboration.csv)
- [Resource contributions in ego-networks (CSV)](https://github.com/recon-icm/reconqdata/blob/master/data-raw/collaboration.csv)

Data model:

```{r data-model, eval=FALSE, echo=TRUE}
reconqdata:::plot_data_model()
```


## Installation

You can install the released version of reconqdata from [GitHub](https://github.com/recon-icm/reconqdata) with:

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("recon-icm/reconqdata")
```



## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(reconqdata)
## basic example code
```
