---
title: "Data from a qualitative study on collaboration in science"
author: "Michał Bojanowski (Kozminski Univeristy), Dominika Czerniawska (University of Manchester and University of Warsaw), Wojciech Fenrich (University of Warsaw)"
output: 
  github_document:
    toc: true
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
library(reconqdata)

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/recon-icm/reconqdata.svg?branch=master)](https://travis-ci.org/recon-icm/reconqdata)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/recon-icm/reconqdata?branch=master&svg=true)](https://ci.appveyor.com/project/recon-icm/reconqdata)
<!-- badges: end -->

---



This is a dataset 





Data model:

```{r data-model, eval=FALSE, echo=TRUE}
reconqdata:::plot_data_model()
```


## Download links

This is an R package, but you can download the files in CSV format using links below:

- [Nodes and their attributes (CSV)](https://github.com/recon-icm/reconqdata/blob/master/data-raw/nodes.csv)
- [Collaboration ego-networks edgelist (CSV)](https://github.com/recon-icm/reconqdata/blob/master/data-raw/collaboration.csv)
- [Resource contributions in ego-networks (CSV)](https://github.com/recon-icm/reconqdata/blob/master/data-raw/collaboration.csv)



## Installation

This is an R package so you can install it directly from GitHub using:

```{r install, eval=FALSE}
remotes::install_github("recon-icm/reconqdata")
```



## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(reconqdata)
## basic example code
```



## Acknowledgements

Authors thank (Polish) [National Science Centre](https://ncn.gov.pl) for support through SONATA grant 2012/07/D/HS6/01971 for the project *Dynamics of Competition and Collaboration  in Science: Individual Strategies, Collaboration Networks, and Organizational Hierarchies* (http://recon.icm.edu.pl).
