---
title: "Data from a qualitative study on collaboration in science"
author: "Michał Bojanowski (Kozminski Univeristy), Dominika Czerniawska (University of Manchester and University of Warsaw), Wojciech Fenrich (University of Warsaw)"
output: 
  github_document:
    toc: true
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
library(reconqdata)
library(magrittr)
requireNamespace("datamodelr")

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/recon-icm/reconqdata.svg?branch=master)](https://travis-ci.org/recon-icm/reconqdata)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/recon-icm/reconqdata?branch=master&svg=true)](https://ci.appveyor.com/project/recon-icm/reconqdata)
<!-- badges: end -->

---



This is a dataset built from a qualitative study of 40 Individual in-Depth Interviews (IDI) conducted in the period April-August of 2016 as a part of the [RECON](recon.icm.edu.pl) project on collaboration in Polish science. This repository is an R package, but the data is also stored in portable CSV format so that it can be used with any other analytical software.


## Data structure

The data is contained in three tables as shown in the diagram below:

```{r data-model, results="asis", echo=FALSE}
fname <- "man/figures/README-data-model.png"
plot_data_model() %>%
  datamodelr::dm_render_graph(width=800) %>%
  DiagrammeRsvg::export_svg() %>%
  cat(file="dm.svg")
if(!file.exists(fname)) {
  dir.create(dirname(fname), recursive = TRUE)
  file.create(fname)
}
# Write a PNG
magick::image_read_svg("dm.svg") %>%
  magick::image_convert(format="png") %>%
  magick::image_write(path=fname)
unlink("dm.svg")
cat("![](", fname, ")", sep="")
```

### Node data

The `nodes` data frame has

### Collaboration networks

### Resource "flow" networks





## Download links

This is an R package, but you can download the files in CSV format using links below:

- [Nodes and their attributes (CSV)](https://github.com/recon-icm/reconqdata/blob/master/data-raw/nodes.csv)
- [Collaboration ego-networks edgelist (CSV)](https://github.com/recon-icm/reconqdata/blob/master/data-raw/collaboration.csv)
- [Resource contributions in ego-networks (CSV)](https://github.com/recon-icm/reconqdata/blob/master/data-raw/collaboration.csv)



## Installation

This is an R package so you can install it directly from GitHub using:

```{r install, eval=FALSE}
remotes::install_github("recon-icm/reconqdata")
```






## Acknowledgements

Authors thank (Polish) [National Science Centre](https://ncn.gov.pl) for support through SONATA grant 2012/07/D/HS6/01971 for the project *Dynamics of Competition and Collaboration  in Science: Individual Strategies, Collaboration Networks, and Organizational Hierarchies* (http://recon.icm.edu.pl).
