---
title: "Resource inventory^[Authors thank (Polish) National Science Centre for support through SONATA grant 2012/07/D/HS6/01971 for the project Dynamics of Competition and Collaboration in Science: Individual Strategies, Collaboration Networks, and Organizational Hierarchies (http://recon.icm.edu.pl).]"
author: "Michał Bojanowski^[Kozminski University. Corresponding author.], Dominika Czerniawska^[University of Manchester and University of Warsaw.], Wojciech Fenrich^[University of Warsaw.]"
output: 
  html_document:
    toc: true
bibliography: refs.bib
vignette: >
  %\VignetteIndexEntry{resource_inventory}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
library(reconqdata)
library(dplyr)

knitr::opts_chunk$set(
  echo = FALSE,
  error = FALSE,
  warning = FALSE
)
```


# Introduction and format

This document lists inventory of academically-relevant resource types with codes, descriptions and sample quotes. In the next section each resource is documented with:

- Its name in the title of the subsection
- Its code in parentheses
- Short textual description
- Some example quotes identified in the interviews


# Codes and quotes

```{r resinv, results="asis"}
reconqdata:::resource_inventory()
```

# Frequency distribution

Frequency distribution of types of resources. Counts correspond to number of times a particular resource appeared in entire corpus of the interviews.

```{r}
resources %>%
  count(code) %>%
  left_join(reconqdata:::codes, by="code") %>%
  arrange(desc(n)) %>%
  select(
    Resource = label,
    Frequency = n
  ) %>%
    knitr::kable()
```


# References
